Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-15 Grassmannian_cells.tex
added a comment
Minor edits

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\newcommand{\supp}{\operatorname{supp}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

\subsection{Bialynicki-Birula decomposition}
The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
\begin{theorem}\label{thm:bb}
  \cite[Section 4]{bb}
  Let $X^{\C^\ast}=\coprod_{i=1}^r C_i$ be the decomposition of the fixed point set of $X$ into connected components.
  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ containing $C_i$ as a subvariety.
  Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle. 
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

\subsection{Torus Actions}
\label{torusaction}
Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural torus action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$GL_n$ Action on Arrows of $K(n)$}
We begin by observing that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{\alpha_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{\alpha_i})$ with $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{\alpha_j}=N_{\alpha_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$ and $1\le i\le n$, we have
  \[\theta_2\circ (g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{\alpha_j})=\sum\limits_{j=1}^n g_{ij}(N_{\alpha_j}\circ\theta_1)=(g.N)_{\alpha_i}\circ\theta_1\]
  so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

@@

While the reflection functors are not $GL_n(\CC)$-equivariant, they do admit the following twisted equivariance.
\begin{lemma}\label{compatibleGSigma}
  For $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
\end{lemma}
\begin{proof}
  We present all the details for $\Sigma_2$, the proof for $\Sigma_1$ is similar.
  For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{\alpha_i})$, where $M'_2$ fits into the following exact sequence:
  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
  and $M'_{\alpha_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have $g.\Sigma_2(M)=(M_1,M'_2,(g.M')_{\alpha_i})$ with 
  \[(g.M')_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M'_{\alpha_j}=\sum\limits_{j=1}^n g_{ij}(\pi\circ\iota_j)=\pi\circ\sum\limits_{j=1}^n g_{ij}\iota_j=\pi\circ g^T\circ\iota_i.\]
  In particular, we may construct $g.\Sigma_2(M)$ using the following exact sequence:
  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{g^{-T}\circ\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
  i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
\end{proof}

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}

Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M).\]
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(V,W)=\mathbb{A}^{\dim\Hom(W,M/V)}$.

@@

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\[\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}\]
which induces a map between quiver Grassmannians as above:
\[\Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).\]
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},\]
where $\tilde K_m=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\[\Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).\]
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $U\in\Phi_{m,I,j}^{-1}(V,0)$ for some $V\subset\tilde P_m(I,j)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is zero.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0,\quad \Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yeilds $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
\end{proof}

>>>>

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\Att}{\operatorname{Att}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\newcommand{\supp}{\operatorname{supp}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

\subsection{Torus Actions and the Bialynicki-Birula Decomposition}
The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
\begin{theorem}
  \label{thm:bb}
  \cite[Section 4]{bb}
  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is a vector bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
Indeed, we can trivialize each vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.

\subsection{Torus Actions on Quiver Grassmannians}
\label{torusaction}
Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural torus action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$GL_n$ Action on Arrows of $K(n)$}
The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq H_m$.
We begin by observing that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{\alpha_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{\alpha_i})$ with $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{\alpha_j}=N_{\alpha_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$ and $1\le i\le n$, we have
  \[\theta_2\circ (g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{\alpha_j})=\sum\limits_{j=1}^n g_{ij}(N_{\alpha_j}\circ\theta_1)=(g.N)_{\alpha_i}\circ\theta_1\]
  so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

@@

While the reflection functors are not $GL_n(\CC)$-equivariant, they do admit the following twisted equivariance.
\begin{lemma}\label{compatibleGSigma}
  For $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
\end{lemma}
\begin{proof}
  We present all the details for $\Sigma_2$, the proof for $\Sigma_1$ is similar.
  For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{\alpha_i})$, where $M'_2$ fits into the following exact sequence:
  \[\xymatrix@C30pt{0 \ar[r] & M_2 \ar[r]^(.4){\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
  and $M'_{\alpha_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have $g.\Sigma_2(M)=(M_1,M'_2,(g.M')_{\alpha_i})$ with 
  \[(g.M')_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M'_{\alpha_j}=\sum\limits_{j=1}^n g_{ij}(\pi\circ\iota_j)=\pi\circ\sum\limits_{j=1}^n g_{ij}\iota_j=\pi\circ g^T\circ\iota_i.\]
  In particular, we may construct $g.\Sigma_2(M)$ using the following exact sequence:
  \[\xymatrix@C50pt{0 \ar[r] & M_2 \ar[r]^(.45){g^{-T}\circ\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
  i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
\end{proof}

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}
Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M).\]
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(V,W)=\mathbb{A}^{\dim\Hom(W,M/V)}$.

@@

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\[\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}\]
which induces a map between quiver Grassmannians as above:
\[\Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).\]
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},\]
where $\tilde K_m=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\[\Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).\]
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is zero.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0,\quad \Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
\end{proof}
